---
title: "GSS challange More Data"
author: "Gil Felix"
date: "Summer 2023"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

To start of I will my data with tigerstat. Next I will put this data in a barchart to distinguish who is in favor and who opposes. I run test to determine the accuracy in my data and so I can be able to explain myself more specifically using numbers.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")

```
In the graph we see that the white race favors capital punishment significantly more than the other races. On the contrary the black race oppose capital punishment more than other races. The other races do accept captital punishment more than they oppose it but the graph shows a good percent of them are in favor of it. 

## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```
As we can see in this numerical summary 65.10% of the white race is in favor of capital punishment therefore the majoirty of of them are in favor, they also have the lowest people to oppose it at 34.90%. Although a majority of the black race opposes it they have 42.63% of their people who accpet it. The other races have a more similar favor and opposition. 

## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
````
The low P value tells us that something weird is occuring within the data.

```{r}
fisherXY(mydata$race,mydata$cappun)
```
Every race is different from every other race in regards to accepting capital punishment or not in this particular data. 

## More data version


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
